### 2017-06-01 paper/documents/4.experiment.tex
- change manuscript structure
- update paper

\section{EXPERIMENTS}
\label{sec:exp}
This is experiment

\subsection{Dataset}
\label{sec:dataset}

This is dataset

\subsection{Results and Discussion}
\label{subsec:results}

This is results and discussion

>>>>

\section{Experiments}
\label{sec:exp}

\subsection{Data Collection}
\label{sec:datacollection}

We are using ROpenDota by Rosdyana Kusuma to built our data set. ROpenDota is an API wrapper service for OpenDota in R. We labeling players from replay and the replay based on The International 2016 and Kiev Major, which contains 8419 labeled players. Using replay data from professional players will guarantee our data set from low level data.

\subsection{Attribute Construction and Evaluation}
\label{sec:attconsandeval}
Attributes for evaluation is presented in table 1.

\subsection{Space and Movement}
\label{spaceandmovement}
Most of player roles depend on the lane (see figure x) which is the most active in the early game.
